Properties and Bayesian fitting of restricted Boltzmann machines

### 2018-09-18 writing/paper-rbm/paper.Rmd
ready for submission

options(
  dplyr.print_min = 6, dplyr.print_max = 6, width = 70,
  digits = 3,
  bookdown.post.latex = fix_envs
)
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  echo = FALSE
)

ggplot2::theme_set(ggplot2::theme_bw(base_family="serif"))

>>>>

options(
  dplyr.print_min = 6, dplyr.print_max = 6, width = 70,
  digits = 3,
  bookdown.post.latex = fix_envs
)
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  echo = FALSE,
  dev = 'postscript'
)

ggplot2::theme_set(ggplot2::theme_bw())
